---
title: "LIS Care Work vs Non Care Work Descriptive Trends"
author: "David Park"
date: "8/15/2019"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r begin, include=FALSE, echo=FALSE, message=FALSE}

lisdata <- read.csv("LIS Results.csv", stringsAsFactors = FALSE)

lisdata <- lisdata[!is.na(lisdata$Mean.Income...Carework),]

# convert from percentage to number
lisdata$Freq...Carework <- as.numeric(substr(lisdata$Freq...Carework,0,nchar(lisdata$Freq...Carework)-1))

lisdata$Freq...Non.Carework <- as.numeric(substr(lisdata$Freq...Carework,0,nchar(lisdata$Freq...Non.Carework)-1))

lisdata$Freq...Non.Carework <- as.numeric(substr(lisdata$Freq...Carework,0,nchar(lisdata$Freq...Non.Carework)-1))

# plot graphs function
create_plots <- function(countryname) {
  
  data_broad <- lisdata[lisdata$Country==countryname & lisdata$Carework=="Broad" ,]
  
  data_concise <- lisdata[lisdata$Country==countryname & lisdata$Carework=="Concise",]
  
  # create time series objects

  plot_broad_size <- data_broad$Freq...Carework
  
  broad_years <- data_broad$Year
  
  plot_broad_inc_care <- data_broad$Mean.Income...Carework
  
  plot_broad_inc_non <- data_broad$Mean.Income...Non.Carework
  
  minincome <- min(data_broad$Mean.Income...Carework, data_broad$Mean.Income...Non.Carework)
  
  maxincome <- max(data_broad$Mean.Income...Carework, data_broad$Mean.Income...Non.Carework)
  
  minperc <- min(data_broad$Freq...Carework, data_broad$Freq...Non.Carework)
  
  maxperc <- max(data_broad$Freq...Carework, data_broad$Freq...Non.Carework)
  
  minyear <- min(data_broad$Year)
  
  maxyear <- max(data_broad$Year)

  if (nrow(data_concise)!=0) {
    
    plot_concise_size <- data_concise$Freq...Carework
    
    concise_years <- data_concise$Year
  
    plot_concise_inc_care <- data_concise$Mean.Income...Carework
  
    plot_concise_inc_non <- data_concise$Mean.Income...Non.Carework
    
    minincome_concise <- min(data_concise$Mean.Income...Carework, data_broad$Mean.Income...Non.Carework)
  
    maxincome_concise <- max(data_concise$Mean.Income...Carework, data_concise$Mean.Income...Non.Carework)
    
    minperc_concise <- min(data_concise$Freq...Carework, data_concise$Freq...Non.Carework)
  
    maxperc_concise <- max(data_concise$Freq...Carework, data_concise$Freq...Non.Carework)
    
    minincome <- min(minincome, minincome_concise)
    
    maxincome <- max(maxincome, maxincome_concise)
    
    minperc <- min(minperc, minperc_concise)
    
    maxperc <- max(maxperc, maxperc_concise)
  }

  #plot graphs
  
  if (nrow(data_concise)==0) {
    
    plot(broad_years, plot_broad_size, type="l", xlab="Year", ylab="Care Work Industry Size (%)", col="red", xlim=c(minyear, maxyear), ylim=c(minperc, maxperc))
    title(main=sprintf("Percentage of %s's care work industry size relative to total industry size (broad)", unique(data_broad$Country)), cex.main=0.75)

    plot(broad_years, plot_broad_inc_care, col="red", type="l", xlab="Year",ylab= unique(data_broad$Currency), ylim=c(minincome, maxincome), xlim=c(minyear, maxyear))
    title(main=sprintf("%s's average personal Labour income in care work industry (broad)", unique(data_broad$Country)), cex.main=0.75)
    lines(broad_years, plot_broad_inc_non, type="l", col="blue")
    legend("bottomright",legend=c("Broad Care","Broad Non Care"),col=c("red","blue"),lty=1:1)
    
  } else {
  plot(broad_years, plot_broad_size, col="red", type="l", xlab="Year",ylab= "Care Work Industry Size (%)", xlim=c(minyear, maxyear), ylim=c(minperc, maxperc))
  title(main=sprintf("Percentage of %s's care work industry size relative to total industry size (broad,concise)", unique(data_broad$Country)),cex.main=0.75)
  lines(concise_years, plot_concise_size, type="l", col="lightpink")
  legend("bottomright",legend=c("Broad","Concise"),col=c("red","lightpink"),lty=1:1)

  plot(broad_years, plot_broad_inc_care, col="red", type="l", xlab="Year", ylab=unique(data_broad$Currency), ylim=c(minincome, maxincome), xlim=c(minyear, maxyear))
  title(main=sprintf("%s's average personal Labour income in care work industry (broad,concise) ", unique(data_broad$Country)), cex.main=0.75)
  lines(broad_years, plot_broad_inc_non, type="l", col="blue")
  lines(concise_years, plot_concise_inc_care, type="l", col="lightpink")
  lines(concise_years, plot_concise_inc_non, type="l", col="lightblue")
legend("bottomright",legend=c("Broad Care", "Broad Non Care", "Concise Care", "Concise Non Care"),col=c("red", "blue", "lightpink", "lightblue"),lty=1:1)
  }
}
```

# Australia

```{r australia, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Australia")
```

# Austria

```{r austria, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Austria")
```

# Belgium 

```{r belgium, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Belgium")
```

# Brazil 

```{r brazil, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Brazil")
```

# Chile

```{r chile, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Chile")
```

# Columbia

```{r columbia, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Columbia")
```

# Czech Republic

```{r czech republic, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Czech Republic")
```

# Denmark

```{r denmark, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Denmark")
```

# Dominican Republic

```{r dominican republic, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Dominican Republic")
```

# Egypt

```{r egypt, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Egypt")
```

# Estonia

```{r estonia, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Estonia")
```

# Finland

```{r finland, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Finland")
```

# France

```{r france, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("France")
```

# Georgia

```{r georgia, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Georgia")
```

# Germany

```{r germany, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Germany")
```

# Greece

```{r greece, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Greece")
```

# Guatemala

```{r guatemala, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Guatemala")
```

# Hungary

```{r hungary, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Hungary")
```

# Iceland

```{r iceland, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Iceland")
```

# India

```{r india, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("India")
```

# Ireland

```{r ireland, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Ireland")
```

# Israel

```{r israel, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Israel")
```

# Italy

```{r italy, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Italy")
```

# Ivory Coast

```{r ivory coast, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Ivory Coast")
```

# Japan

```{r jp, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Japan")
```

# Lithuania

```{r lit, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Lithuania")
```

# Luxembourg

```{r lux, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Luxembourg")
```

# Mexico

```{r mex, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Mexico")
```

# Netherlands

```{r net, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Netherlands")
```

# Norway

```{r norway, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Norway")
```

# Panama

```{r pan, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Panama")
```

# Paraguay

```{r par, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Paraguay")
```

# Peru

```{r peru, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Peru")
```

# Poland

```{r poland, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Poland")
```

# Russia

```{r rus, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Russia")
```

# Serbia

```{r serbia, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Serbia")
```

# Slovakia

```{r slo, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Slovakia")
```

# South Africa

```{r southa, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("South Africa")
```


# Spain

```{r spain, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Spain")
```

# Sweden

```{r sweden, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Sweden")
```

# Switzerland

```{r swit, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Switzerland")
```

# Taiwan

```{r tai, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Taiwan")
```

# United States

```{r us, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("United States")
```

# Uruguay

```{r uruguay, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Uruguay")
```

# Vietnam

```{r vietnam, echo=FALSE, message=FALSE,warning=FALSE}
create_plots("Vietnam")
```

# Sweden, Italy, U.S.

```{r combined, echo-FALSE, message=FALSE, warning=FALSE}

  data_broad <- lisdata[(lisdata$Country=="Sweden" | lisdata$Country=="Italy" | lisdata$Country=="United States") & lisdata$Carework=="Broad",]

  plot_broad_size_Sweden <- data_broad[data_broad$Country=="Sweden", data_broad$Freq...Carework]
  
  plot_broad_size_Italy <- data_broad[data_broad$Country=="Italy", data_broad$Freq...Carework]
  
  plot_broad_size_US <- data_broad[data_broad$Country=="United States", data_broad$Freq...Carework]
  
  broad_years <- data_broad$Year
  
  plot_broad_inc_care <- data_broad$Mean.Income...Carework
  
  plot_broad_inc_non <- data_broad$Mean.Income...Non.Carework
  
  minincome <- min(data_broad$Mean.Income...Carework, data_broad$Mean.Income...Non.Carework)
  
  maxincome <- max(data_broad$Mean.Income...Carework, data_broad$Mean.Income...Non.Carework)
  
  minperc <- min(data_broad$Freq...Carework, data_broad$Freq...Non.Carework)
  
  maxperc <- max(data_broad$Freq...Carework, data_broad$Freq...Non.Carework)
  
  minyear <- min(data_broad$Year)
  
  maxyear <- max(data_broad$Year)

plot(broad_years, plot_broad_size, type="l", xlab="Year", ylab="Care Work Industry Size (%)", col="red", xlim=c(minyear, maxyear), ylim=c(minperc, maxperc))
    title(main=sprintf("Percentage of %s's care work industry size relative to total industry size (broad)", unique(data_broad$Country)), cex.main=0.75)

    plot(broad_years, plot_broad_inc_care, col="red", type="l", xlab="Year",ylab= unique(data_broad$Currency), ylim=c(minincome, maxincome), xlim=c(minyear, maxyear))
    title(main=sprintf("%s's average personal Labour income in care work industry (broad)", unique(data_broad$Country)), cex.main=0.75)
    lines(broad_years, plot_broad_inc_non, type="l", col="blue")
    legend("bottomright",legend=c("Broad Care","Broad Non Care"),col=c("red","blue"),lty=1:1)




```


